### 2016-11-10 datamining/summery.tex
Fitted count stuff

To estimate the joint distrubtion of $X$ and $Y$ we use $\overset{\wedge}{P}(x,y)=\frac{n(x,y)}{n}$

>>>>

To estimate the joint distrubtion of $X$ and $Y$ we use
$\overset{\wedge}{P}(x,y)=\frac{n(x,y)}{n}$
\subsection{Fitted counts}
These are simply obtained by multiplying
the estimated probabilities with the total number of observations. 
To determine whether the independence assumption is justified, we compare the
observed counts with the fitted counts of the independence model.
